Environmental behaviour & practices

### 2021-01-19 02-supply-chain.Rmd
lucid chart update

:::l-page
<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
:::

>>>>

:::l-page
<div style="width: 100%; height: 480px; margin: 10px; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:95%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="Nb17wGQ7otTB"></iframe></div>
:::

### 2021-01-19 03-comportements.Rmd
adding link to the lucidchart
lucid chart update

:::l-page
<div style="width: 100%; height: 480px; margin: 10px; position: relative;"><iframe allowfullscreen frameborder="0" style="width:640px; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="rc17nDan15JX"></iframe></div>
:::

>>>>

[**Link to modify the Graph**](https://lucid.app/lucidchart/invitations/accept/f6847ab0-3fd4-4749-a581-669058760d2d)

:::l-page
<div style="width: 100%; height: 480px; margin: 10px; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:95%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="rc17nDan15JX"></iframe></div>
:::
